---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


To properly use this package the user will have to download data files from US-NHTSA Fatality Analysis Reporting System (FARS) and place them in the working directory of the project. Please see the [NHTSA](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) website to access the data. 

Once you have collected the data you are interested in use, please save the files into the working directory or change the working directory before using the FARS tools. It is important that the filenames are not changed when saved locally. The file should match the format below

file format:
*accident_**year**.csv.bz2*

Once the data files have been saved to a directory, supply the years that you would like to summarize to the fars_summarize_years function.

```{r echo=TRUE, eval=FALSE}
farstools::fars_summarize_years(2013:2015)
```




To use the Fars_map_state function you must supply a year and stateID number so that the funciton can plot the data across the map of a state. The state ID can be found at the [U.S. Census](https://www.census.gov/geo/reference/ansi_statetables.html) website.

```{r fig.cap="FARS MAP output", fig.align='left', eval=FALSE}
farstools::fars_map_state(39, 2014)
```
