---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To properly use this package the user will have to download data files from US-NHTSA Fatality Analysis Reporting System (FARS) and place them in the working directory of the project. Please see the [NHTSA](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) website to access the data. 

Once you have collected the data you are interested in use, please save the files into the working directory or change the working directory before using the FARS tools. It is important that the filenames are not changed when saved locally. The file should match the format below

file format:
*accident_**year**.csv.bz2*

Once the data files have been saved to a directory, supply the years that you would like to summarize to the fars_summarize_years function.

```{r eval = FALSE}
fars_summarize_years(2013:2015)
```

which will produce a tibble similiar to below.

# A tibble: 12 x 4
   MONTH `2013` `2014` `2015`
   <int>  <int>  <int>  <int>
 1     1   2230   2168   2368
 2     2   1952   1893   1968
 3     3   2356   2245   2385
 4     4   2300   2308   2430
 5     5   2532   2596   2847
 6     6   2692   2583   2765
 7     7   2660   2696   2998
 8     8   2899   2800   3016
 9     9   2741   2618   2865
10    10   2768   2831   3019
11    11   2615   2714   2724
12    12   2457   2604   2781

